---
title: "Pleasent rating of odor molecules alone vs binary mixture with gammaHeptalactone"
author: "Dhirendra Singh Gehlot"
date: '2022-04-21'
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages
```{r import}
library(pyrfume)
library(dplyr)
library(plotly)
```

#Import dataset from pyrfume database
```{r import}
ma <- load_data("ma_2021/behavior.csv")
molecule_name <- load_data("ma_2021/molecules.csv")
View(ma)
summary(ma)
```

#find most used odor for creating a binary mixture from the df
```{r}
#define a mode function
my_mode <- function(x) {                      
  unique_x <- unique(x)
  tabulate_x <- tabulate(match(x, unique_x))
  unique_x[tabulate_x == max(tabulate_x)]
}

my_mode(ma$CID.A)
ma_gammaHeptalactone<-subset(ma, ma$CID.A == "7742")
```

#rename the CID number of the odor compounds with their common name
#odor discription of gammaHeptalactone: sweet spicy herbal hay coumarin
```{r}
ma_gammaHeptalactone$CID.A[ma_gammaHeptalactone$CID.A == "7742"] <- "gammaHeptalactone"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "998"] <- "phenylacetaldehyde"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "7284"] <- "2-methylbutyraldehyde"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "7438"] <- "carveol"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "7714"] <- "gamma-undecalactone"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "7749"] <- "ethyl propionate"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "7765"] <- "acetal"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "8186"] <- "undecanal"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "10976"] <- "2-heptanol"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "12748"] <- "4-methylthiazole"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "18635"] <- "3-(methylthio)propionaldehyde"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "18827"] <- "1-octen-3-ol"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "31249"] <- "diethyl succinate"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "61592"] <- "ethyl 3-methylsulfanylpropanoate"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "78126"] <- "2-phenylethanethiol"
ma_gammaHeptalactone$CID.B[ma_gammaHeptalactone$CID.B == "637758"] <- "ethyl cinnamate"

summary(ma_gammaHeptalactone)
```

#create a df contanining mean pleasentness ratings of odor molecules alone and in binary mixture with gammaHeptalactone
```{r}
#calculate mean for pleasentness rating for each molecule in column CID.B
mean_PB <- aggregate(PB ~ CID.B, data = ma_gammaHeptalactone, FUN = mean)    #when presented alone
mean_PAB <- aggregate(PAB ~ CID.B, data = ma_gammaHeptalactone, FUN = mean)  #presented in binary mixture

PB <- as.data.frame(mean_PB)
PAB <- as.data.frame(mean_PAB)

#single df containing mean pleasentness rating of just individual odor compound and in mixture with gammaHeptalactone
PB_PAB <- left_join(PB, PAB, by = "CID.B")
colnames(PB_PAB) <- c("Molecules", "Alone", "Binary.gammaHeptalactone") #rename the column names
```

#plot the bargraph
```{r}
fig <- plot_ly(PB_PAB, x = ~ Molecules, y = ~ Alone, type = 'bar', name = 'Alone')
fig <- fig %>% add_trace(y = ~ Binary.gammaHeptalactone, name = 'Binary.gammaHeptalactone')
fig <- fig %>% layout(yaxis = list(title = 'Pleasentness rating'), title = "Pleasentness rating of Molecules alone vs Binary mixture with gammaHeptalactone", barmode = 'group')
fig

```








